Relationships in the extremes and their influence on competition and coexistence

### 2021-12-20 paper/Paper.Rnw
adding results and caption fig 6

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig4.pdf}
\caption{ATAs can sometimes make the difference between species coexistence and exclusion of the weaker
competitor; both ``ATA rescue'' and ``ATA exclusion'' (see Methods) are possible. 
All panels show the IGR, the ATA term of the extended MCT [$\Delta_i^{[E || C]}$ in equation 
(\ref{eq:full_decomp})], and the difference of these quantities. 
For each panel, $\delta$ and $\sigma$ are fixed at values specified in the 
margins, and the three quantities are plotted against $\mu_1-\mu_2$ to isolate points in the
``trait-difference space'' corresponding to ATA rescue 
($\psi_{\text{ATA}}(\delta,\sigma) \setminus \psi_{\lnot\text{ATA}}(\delta,\sigma)$) 
or ATA exclusion ($\psi_{\lnot\text{ATA}}(\delta,\sigma) \setminus \psi_{\text{ATA}}(\delta,\sigma)$; 
see Methods). Values of $\mu_1-\mu_2$ for which the IGR is positive but 
$\text{IGR}-\Delta_i^{[E || C]}$ is negative correspond to ATA rescue (shaded yellow), whereas
values of $\mu_1-\mu_2$ for which the IGR is negative but $\text{IGR}-\Delta_i^{[E || C]}$ is positive 
correspond to ATA exclusion (shaded violet). Top panels also include domains
of ATA rescue or exclusion, but they were too narrow to be highlighted by shading and are
probably of minimal practical importance. 
Standard errors of plotted quantities were never greater than \Sexpr{round(se4,5)}, 
so are not displayed. The dashed red line on panel L corresponds to the parameters
used for Fig. \ref{fig:pedagog}. This plot uses $q_{ij}=1$. An analogous plot was generated 
using $q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$, but it looked exactly the same, by mathematical necessity (see SI section \ref{SI-sect:F4andqij}).}\label{fig:fig4}
\end{figure}
%***DAN: Dan has edited this caption

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig6.pdf}
\caption{} \label{fig:fig6}
\end{figure}

>>>>

%G4
Fulfilling goal G4 of the Introduction (to provide an empirical example of species coexistence which highlights the role ATAs can play), Fig. \ref{fig:fig5} and Fig. \ref{fig:fig6} 
show that the ATA contributions have magnitude comparable to the 
magnitudes of other terms of the extended MCT decomposition and 
parameters subspaces exist where ATA rescue occurs. 
Within the investigated parameters of Fig.\ref{fig:fig5}, ATA contribution, $\Delta_i^{[EC]}$, 
is always positive, even in cases where IGR is negative, and is almost always second to 
the contribution of varying environment, $\Delta_i^{E}$, 
including for the original coexistence parameters specified in Gonzalez Decamps.  
Fig.\ref{fig:fig5} plots the various contributions of coexistence (see eq. \ref{eq:full_decomp}) for different varying parameters with two of the three parameters set constant in each plot. Increasing amplitude and mean temperature showed increasing trends in the IGR and decomposed quantities, while increasing periods showed less change.

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig4.pdf}
\caption{ATAs can sometimes make the difference between species coexistence and exclusion of the weaker
competitor; both ``ATA rescue'' and ``ATA exclusion'' (see Methods) are possible. 
All panels show the IGR, the ATA term of the extended MCT [$\Delta_i^{[E || C]}$ in equation 
(\ref{eq:full_decomp})], and the difference of these quantities. 
For each panel, $\delta$ and $\sigma$ are fixed at values specified in the 
margins, and the three quantities are plotted against $\mu_1-\mu_2$ to isolate points in the
``trait-difference space'' corresponding to ATA rescue 
($\psi_{\text{ATA}}(\delta,\sigma) \setminus \psi_{\lnot\text{ATA}}(\delta,\sigma)$) 
or ATA exclusion ($\psi_{\lnot\text{ATA}}(\delta,\sigma) \setminus \psi_{\text{ATA}}(\delta,\sigma)$; 
see Methods). Values of $\mu_1-\mu_2$ for which the IGR is positive but 
$\text{IGR}-\Delta_i^{[EC]}$ is negative correspond to ATA rescue (shaded yellow), whereas
values of $\mu_1-\mu_2$ for which the IGR is negative but $\text{IGR}-\Delta_i^{[EC]}$ is positive 
correspond to ATA exclusion (shaded violet). Top panels also include domains
of ATA rescue or exclusion, but they were too narrow to be highlighted by shading and are
probably of minimal practical importance. 
Standard errors of plotted quantities were never greater than \Sexpr{round(se4,5)}, 
so are not displayed. The dashed red line on panel L corresponds to the parameters
used for Fig. \ref{fig:pedagog}. This plot uses $q_{ij}=1$. An analogous plot was generated 
using $q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$, but it looked exactly the same, by mathematical necessity (see SI section \ref{SI-sect:F4andqij}).}\label{fig:fig4}
\end{figure}
%***DAN: Dan has edited this caption

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig6.pdf}
\caption{The degree of ATA contribution to the IGR change with parameters of temperature oscillation. The ratio $\Delta_i^{[EC]}/IGR$ constitutes the degree of ATA contribution to thee IGR with larger magnitudes signifying larger ATA contributions. In this model, for the plotted parameters, positive $\Delta_i^{[EC]}/IGR$ only result from positive $\Delta_i^{[EC]}$ and positive $IGR$ and negative $\Delta_i^{[EC]}/IGR$ only result from positive $\Delta_i^{[EC]}$ and negative $IGR$. Thus, cyan areas indicate failure to coexist and magenta areas indicate coexistence with ATA contribution increasing with color intensity. The most intense areas of magenta indicate parameter subspaces where ATA rescue occurs. For simplicity and readability magnitudes of $\Delta_i^{[EC]}/IGR$ >1 are capped at $\abs{1}$. } \label{fig:fig6}
\end{figure}
